---
date: "`r Sys.Date()`"
author: "Byron C. Jaeger"
title: "Mortality/graft loss prediction using CHD diagnosis data"
output: 
  officedown::rdocx_document:
    mapstyles:
      Normal: ['First Paragraph']
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)

library(officedown)
library(officer)
library(flextable)
library(tidyverse)
library(table.glue)
library(targets)

tar_load(tidyselect::matches('^tbl|^fig'))

```

Hello again!

\newpage
__Table 1__: Characteristics of patients at listing

```{r}
tbl_chars_waitlist$table
```

\newpage
__Table 2__: Characteristics of patients at transplant

```{r}
tbl_chars_posttxpl$table
```

\newpage
__Table 3__: Hazard ratios (95% confidence interval) for mortality within 1 year of listing among patients with congenital heart disease versus cardiomyopathy

```{r}
tbl_mdl_waitlist$chd
```

\newpage
__Table 4__: Hazard ratios (95% confidence interval) for mortality within 1 year of listing among patients with cardiomyopathy versus congenital heart disease.

```{r}
tbl_mdl_waitlist$cmy
```

\newpage
__Table 5__: Hazard ratios (95% confidence interval) for mortality or graft loss within 1 year of transplant among patients with congenital heart disease versus cardiomyopathy

```{r}
tbl_mdl_posttxpl$chd
```

\newpage
__Table 6__: Hazard ratios (95% confidence interval) for mortality or graft loss within 1 year of transplant among patients with cardiomyopathy versus congenital heart disease.

```{r}
tbl_mdl_posttxpl$cmy
```


\newpage
__Table 7__: Area underneath the receiver operator characteristic curve when using variables in the existing UNOS risk model versus additional diagnostic variables. 
```{r}
tbl_mccv$auc
```

\newpage
__Table 8__: P-value for poor calibration when using variables in the existing UNOS risk model versus additional diagnostic variables. 
```{r}
tbl_mccv$gnd
```

\newpage
__Table 9__: Index of prediction accuracy when using variables in the existing UNOS risk model versus additional diagnostic variables. 
```{r}
tbl_mccv$ipa
```

\newpage
__Figure 1__: Cumulative incidence of mortality within 1 year of listing

```{r}
fig_kaplan_waitlist
```

\newpage
__Figure 2__: Cumulative incidence of mortality within 1 year of listing, stratified by listing year.

```{r}
fig_kaplan_by_year$waitlist
```

\newpage
__Figure 3__: Cumulative incidence of mortality or graft loss within 1 year of transplant

```{r}
fig_kaplan_posttxpl
```

\newpage
__Figure 4__: Cumulative incidence of mortality within 1 year of listing, stratified by listing year.

```{r}
fig_kaplan_by_year$posttxpl
```

